My title

### 2024-02-15 outputs/paper/paper.qmd
adding

# Data {#sec-data}
```{r}
file_path <- "../../outputs/data/bully_clean_data.csv"
bully_clean_data <- read.csv(file_path)
bully_clean_data$date <- as.Date(bully_clean_data$date)
sample_data <- head(bully_clean_data, 6)
```

@@

```{r}

>>>>

# Data {#sec-data}
```{r}
file_path <- "../../outputs/data/bully_clean_data.csv"
bully_clean_data <- read.csv(file_path)
bully_clean_data$date <- as.Date(bully_clean_data$date)
NY_pop_2019_clean<- read.csv("../../outputs/data/NY_pop_2019_clean.csv")
NY_pop_2020_clean<- read.csv("../../outputs/data/NY_pop_2020_clean.csv")
NJ_pop_2019_clean<- read.csv("../../outputs/data/NJ_pop_2019_clean.csv")
NJ_pop_2020_clean<- read.csv("../../outputs/data/NJ_pop_2020_clean.csv")
LA_pop_2019_clean<- read.csv("../../outputs/data/LA_pop_2019_clean.csv")
LA_pop_2020_clean<- read.csv("../../outputs/data/LA_pop_2020_clean.csv")
sample_data <- head(bully_clean_data, 6)
```

@@

```{r}
data %>%
  arrange(desc(pop)) %>%
  mutate(country = factor(country)) %>%
  ggplot(aes(x=gdpPercap, y=lifeExp, size = pop)) +
    geom_point(alpha=0.5) +
    scale_size(range = c(.1, 24), name="Population (M)")
```
